Forecasting the 2024 US Presidential Election

### 2024-11-04 paper/paper.qmd
Minor fixes in appendix A

## Appendix A: Pollster Methodology Overview {-}
Emerson College Polling was initially a college polling exercise and is now an "innovative, nationally-ranked" non-partisan polling center (@AboutUs). For the 2024 USA Presidential Election pollster, the Emerson College Polling defined the population to be "likely voters" of 2024 United States Presidential Election. Emerson College Polling does indicate that the targeted population of "likely voters" is based on "2024 Likely Voter Modeling." However, the methodology for this modelling and the specific model is not indicated, so the specific validity of the targeted population cannot be determine (@Polling).

@@

From the methodology of recruiting people indicated in the previous paragraph, we can see that while the targeted population of the national poll are likely voters, the sampling frame are likely voters that use phones, either mobile or landline. Emerson College Polling chooses 1000 samples from their targeted population, in this case is all likely voters of the 2024 United States Presidential Election, and it is then "weighted by gender, education, race, age, party affiliation, and region based on 2024 likely voter modeling" (@Polling) for each national poll. As most people in the United States use phones by some means, the target population and sampling frame are highly similar, increasing the overall validity of the survey.

In the "MMS-to-Online" and "IVR(Interactive Voice Response)" approaches, random sampling is used, and in the "Online Opt-in Panel" approach, there is no indication of a specific sampling approach (@AboutUs). We can conclude that the general approach used in this specific pollster is random sampling. Random sampling tends to reduce bias, simplify analysis, and is also easy to implement, but at the same time also requires much time and money. In consideration with the sample size of 1000 people compared to the targeted population of likely voters, which contains most of the population of the United States of America, there is a high possibility of existing selection bias, occurring when the participants are not representative of the population.

There is also no specific indication of how non-response is treated, but the results section of national polls, such as the one from September 29 to October 1, 2024, implicates that non-response are eliminated from final recorded results of the survey. Therefore, we cannot ignore the possibility of non-response bias, occurring when non-respondents differ significantly from respondents. For example, such non-response bias occurs when non-respondents are from California, while respondents are from other states except California.

The questionnaire set by Emerson College Polling for this survey, based on the national polls set from September 29 to October 1, 2024, compose mostly of questions with most common choices listed as choices, and also allowing participants to type in their own answer if it is not included in the list of most common choices. The questionnaire is generally written in an objective voice, and all questions only allow participants to make only one choice. All questions in the questionnaire are relatively-common, including ones about ethnicity, age range, region, and education which collects demographical data, and ones that are related to actual presidential-election predictions, including opinions about Joe Biden's performance, the two major parties (Democratic and Republican), whether s/he would vote, and voting inclinations. The only issue observed in the questionnaire is that it is too lengthy, containing more than 20 questions, which may decrease participants' motivations to complete the survey, even after starting it (@Polling).

>>>>

## Appendix A: Pollster Methodology Overview {-}
Emerson College Polling was initially a college polling exercise and is now an "innovative, nationally-ranked" non-partisan polling center (@AboutUs). For the 2024 USA Presidential Election pollster, the Emerson College Polling defined the population to be "likely voters" of 2024 United States Presidential Election. Emerson College Polling does indicate that the targeted population of "likely voters" is based on "2024 Likely Voter Modeling." However, the methodology for this modelling and the specific model is not indicated, so the specific validity of the targeted population cannot be determined (@Polling).

@@

From the methodology of recruiting people indicated in the previous paragraph, we can see that while the targeted population of the national poll are likely voters, the sampling frame are likely voters that use phones, either mobile or landline. Emerson College Polling chooses 1000 samples from their targeted population of likely voters of the 2024 United States Presidential Election, and it is then "weighted by gender, education, race, age, party affiliation, and region based on 2024 likely voter modeling" (@Polling) for each national poll. As most people in the United States use phones by some means, the target population and sampling frame are highly similar, increasing the overall validity of the survey.

In the "MMS-to-Online" and "IVR(Interactive Voice Response)" approaches, random sampling is used, and in the "Online Opt-in Panel" approach, there is no indication of a specific sampling approach (@AboutUs). We can conclude that the general approach used in this specific pollster is random sampling. Random sampling tends to reduce bias, simplify analysis, and is also easy to implement, but at the same time also requires much time and money. In consideration with the sample size of 1000 people compared to the targeted population of likely voters, which contains most of the population of the United States of America, there is a high possibility of existing selection bias occurring when the participants are not representative of the population.

There is also no specific indication of how non-response is treated, but the results section of national polls, such as the one from September 29 to October 1, 2024, implicates that non-response are eliminated from final recorded results of the survey. Therefore, we cannot ignore the possibility of non-response bias occurring when non-respondents differ significantly from respondents. For example, such non-response bias occurs when non-respondents are from California, while respondents are from other states except California.

The questionnaire set by Emerson College Polling for this survey, based on the national polls set from September 29 to October 1, 2024, compose mostly of questions with most common choices listed as choices, and also allowing participants to type in their own answer if it is not included in the list of most common choices. The questionnaire is generally written in an objective voice, and all questions only allow participants to make only one choice. All questions in the questionnaire are relatively-common, including ones about ethnicity, age range, region, and education which collects demographic data, and ones that are related to actual presidential-election predictions, including opinions about Joe Biden's performance, the two major parties (Democratic and Republican), whether s/he would vote, and voting inclinations. The only issue observed in the questionnaire is that it is too lengthy, containing more than 20 questions, which may decrease participants' motivations to complete the survey, even after starting it (@Polling).
